I don't know, are you sure we want to do this?\\ Sea level adaptation decisions under uncertainty

### 2016-11-10 submission/paper.tex
Prob exceed 25cm
Abstract (still needs findings)

\begin{abstract}
...
\end{abstract}

>>>>

\begin{abstract}
Sea level rise has serious consequences for harbor infrastructure, storm drain and sewer systems, and many other issues. Adapting to sea level rise requires comparing different possible adaptation strategies, comparing the cost of different actions (inluding no action), and assessing at what point in time the chosen strategy should be implemented. All these decisions must be made under considerable uncertainty--in the amount of sea level rise, in the cost of adaptation actions, in the cost of no action. We develop two illustrative examples: for Bergen on Noirway's west coast and for Esbjerg on the west coast of Denmark. Different comonents of uncertainty are visualized. {\color{blue} Findings go here}
\end{abstract}
